### 2016-05-19 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
Edits to gas burner report: updated drawings, more content to intro.

% ================
% = Introduction =
% ================
\chapter{Introduction}
\label{chap:Introduction}

% [Brief Introduction of FRD at NIST, ventilation, etc.]

This report describes nine full-scale fire experiments in which the effects of changing the ventilation patterns within a structure were studied. The experiments were conducted in two structures designed to replicate typical residential dwellings. During each test, propane was provided to three diffusion flame burners at a measured flow rate. Local measurements of temperature, gas velocity, heat flux, and gas concentrations were collected at various locations throughout the structure while ventilation patterns within the structure were changed by opening and closing certain doors and vents.

@@

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Dimensioned_Instrumentation}
	\\~\\
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Dimensioned_Instrumentation}
	\caption[Location of instrumentation in the West Structure.]{Location of instrumentation in the second floor (top) and first floor (bottom) of the West Structure.}
	\label{fig:west_instrumentation}
\end{figure}

@@

\multirow{16}{*}{\large{\textbf{A4}}}
 & TC\_A4\_1  & 0.03~m below soffit  & Temperature \\
 & TC\_A4\_2  & 0.30~m below soffit  & Temperature \\
 & TC\_A4\_3  & 0.61~m below soffit  & Temperature \\
 & TC\_A4\_4  & 0.91~m below soffit  & Temperature \\
 & TC\_A4\_5  & 1.22~m below soffit  & Temperature \\
 & TC\_A4\_6  & 1.52~m below soffit  & Temperature \\
 & TC\_A4\_7  & 1.83~m below soffit  & Temperature \\
 & TC\_A4\_8  & 2.13~m below soffit  & Temperature \\
 & BDP\_A4\_1 & 0.03~m below soffit  & Velocity \\
 & BDP\_A4\_2 & 0.30~m below soffit  & Velocity \\
 & BDP\_A4\_3 & 0.61~m below soffit  & Velocity \\
 & BDP\_A4\_4 & 0.91~m below soffit  & Velocity \\
 & BDP\_A4\_5 & 1.22~m below soffit  & Velocity \\
 & BDP\_A4\_6 & 1.52~m below soffit  & Velocity \\
 & BDP\_A4\_7 & 1.83~m below soffit  & Velocity \\
 & BDP\_A4\_8 & 2.13~m below soffit  & Velocity \\

>>>>

% ================
% = Introduction =
% ================
\chapter{Introduction}
\label{chap:Introduction}
% [Brief Introduction of FRD at NIST, ventilation, etc.]
The Fire Fighting Technology Group of the Fire Research Division at the National Institute of Standards and Technology (NIST) develops and applies technology, measurements, and standards to improve the understanding of fire behavior, prevention and suppression, which ultimately enables advances in fire fighting operations, firefighter equipment, fire suppression, fire investigations, and disaster response. One function of the group is to conduct research to enhance the understanding of fire fighting tactics and how they affect the fire environment.

The development and behavior of compartment fires, such as a fire inside a residential structure, depend greatly on the ventilation conditions within the compartment. There are a variety of tactics used by firefighters that can affect the ventilation of a fire environment. For example, firefighters may open different doors and windows within a structure or cut holes in a structure's roof with the intention of removing hot gases and smoke from the structure's interior and introducing fresh, cool air into the environment. Additionally, firefighters sometimes employ a tactic known as ``positive pressure attack'' (PPA) or ``positive pressure ventilation'' (PPV) on the fire ground in an attempt to improve the tenability of the fire environment. PPA/PPV involves using a fan aimed at an opening of a structure and is intended to force fresh, exterior air through the opening into the structure and exhaust hot gases and smoke out of the structure through a separate vent. Nine full-scale fire experiments were performed to study how these tactics affect ventilation within a structure. The tests were conducted in two structures designed to replicate typical residential dwellings. During each experiment, propane was provided to three diffusion flame burners at a measured flow rate. Local measurements of temperature, gas velocity, heat flux, and gas concentrations were collected at various locations throughout the structure while the ventilation within the structure was varied by opening and closing certain doors and vents. During a number of the tests, a PPV fan was used in conjunction with the opening and closing of vents to further affect the ventilation conditions within the fire environment. This report contains in-depth descriptions of the setup and procedure used for each of the nine experiments.

@@

\begin{figure}[!ht]
	\includegraphics[width=0.94\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Dimensioned_Instrumentation}
	\\~\\
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Dimensioned_Instrumentation}
	\caption[Location of instrumentation in the West Structure.]{Location of instrumentation in the second floor (top) and first floor (bottom) of the West Structure.}
	\label{fig:west_instrumentation}
\end{figure}

@@

% \multirow{16}{*}{\large{\textbf{A4}}}
%  & TC\_A4\_1  & 0.03~m below soffit  & Temperature \\
%  & TC\_A4\_2  & 0.30~m below soffit  & Temperature \\
%  & TC\_A4\_3  & 0.61~m below soffit  & Temperature \\
%  & TC\_A4\_4  & 0.91~m below soffit  & Temperature \\
%  & TC\_A4\_5  & 1.22~m below soffit  & Temperature \\
%  & TC\_A4\_6  & 1.52~m below soffit  & Temperature \\
%  & TC\_A4\_7  & 1.83~m below soffit  & Temperature \\
%  & TC\_A4\_8  & 2.13~m below soffit  & Temperature \\
% \cline{2-4}
%  & BDP\_A4\_1 & 0.03~m below soffit  & Velocity \\
%  & BDP\_A4\_2 & 0.30~m below soffit  & Velocity \\
%  & BDP\_A4\_3 & 0.61~m below soffit  & Velocity \\
%  & BDP\_A4\_4 & 0.91~m below soffit  & Velocity \\
%  & BDP\_A4\_5 & 1.22~m below soffit  & Velocity \\
%  & BDP\_A4\_6 & 1.52~m below soffit  & Velocity \\
%  & BDP\_A4\_7 & 1.83~m below soffit  & Velocity \\
%  & BDP\_A4\_8 & 2.13~m below soffit  & Velocity \\
